---
title: "R Notebook"
output: html_notebook
---

```{r}
# **Prepare for the fight**
getwd()
work_dir <- "D:/Szisz/Networks/Assignment/"
setwd(work_dir)
```


```{r}
#**required packages**
library(igraph)
library(dplyr)
```


```{r}
cycling_df <- data.frame(read.csv("networktest.csv", sep = ",", header = TRUE))
print(tail(cycling_df))
```


```{r}
#number of riders
length(unique(cycling_df$rider_name))
# number of races
length(unique(cycling_df$race))
# observed years
table(cycling_df$season)
```
```{r}
# filter data for 2000-2006 (7-year window)
active_data <- subset(cycling_df, season<=2019 & season>=2015)
```
```{r}
# table from the list
mat <- table(active_data$rider_name, active_data$race)

# create an n x n matrix = adjacency matrix
matrix <- mat %*% t(mat)

# set the diagonal to 0
diag(matrix) <- 0

# check the first 10x10 matrix (it is BIG!)
matrix[1:3, 1:3]
```

```{r}
memory.limit()
## To increase the storage capacity
memory.limit(size=30000)
## I did this to increase my storage capacity to 7GB
```

```{r}
# create a graph object
graph_data <- graph.adjacency(matrix, mode='undirected')

# check the graph object
graph_dataiI
```
```{r}
plot(graph_data)
```
```{r}
edge_density(graph_data, loops=F)
```
```{r}
transitivity(graph_data, type="global")  # net is treated as an undirected network
```
```{r}
diameter(graph_data, directed=F)
```

```{r}
deg <- degree(graph_data, mode="all")

plot(graph_data, vertex.size=deg*3)
plot(deg)
```

```{r}
hist(deg)
```
```{r}
centr_clo(graph_data, mode="all", normalized=T) 
```
```{r}
library('sna')
kc<-kcores(mat, mode = "graph", diag = FALSE, cmode = "freeman",
    ignore.eval = FALSE)

#Plot the result
gplot(mat,vertex.col=kc)
# }
```



```{r}
E(graph_data)$weight<-runif(ecount(graph_data), 0, 1)

V(graph_data)$name<-1:vcount(graph_data)

Vcp<-core_periphery_weighted(graph_data,"undirected")

```{r}
# **B) k-core of nodes and edge-betweenness based brokerage for nodes **
```
```{r}
# kcore measure for each node
nodedata <- data.frame(V(graph_data)$name, coreness(graph_data))
colnames(nodedata) <- c("rider_name", "coreness")
```
```{r}
# edge betweenness of ties
ebetw <- edge_betweenness(graph_data)
ebetw[1:10]
print(length(ebetw))
```
```{r}
# set edge betweenness as edge property
E(graph_data)$ebetw <- ebetw
graph_data
```
```{r}
# sum edge betweenness by nodes
betw <- strength(graph_data, weights=ebetw)
betw[1:10]
```
```{r}
# average 
betw <- betw/(degree(graph_data)) 
betw[is.na(betw)] <- 0

# log
betw <- log(betw +1)
```
```{r}
# edge betweenness based brokerage data frame
betw_df <- data.frame(V(graph_data)$name, betw)
colnames(betw_df) <- c("rider_name", "betw")
print(head(betw_df, 5))
```
```{r}
# merge
nodedata <- merge(nodedata, betw_df, by=c("rider_name"))
print(head(nodedata, 10))
```

